Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility

### 2025-11-11 paper/03-methods.qmd
up v2

t1 <- db %>% 
  select(just_pension_f, 
         estrato_orig, 
         estrato_ocupa, 
         educ_orig_f,
         hogar_bip_f, 
         nacionalidad_f, 
         sexo_f,
         m0_edad_f, 
         etnia_f, 
         merit_i,
         wave

>>>>

library(summarytools)
t1 <- db %>% 
  select(just_pension_f, 
         estrato_orig, 
         estrato_ocupa, 
         educ_orig_f,
         hogar_bip_f, 
         nacionalidad_f, 
         sexo_f,
         m0_edad_f, 
         etnia_f, 
         merit_i,
         wave

### 2025-11-11 paper/04-analysis.qmd
up v2

```{r}
#| label: fig-alluvial
#| fig-cap: "Change in preferences for pension commodification over time (2016, 2018, and 2023)."
#| fig-cap-location: bottom
#| echo: false
#| results: asis
g1
```

@@

```{r}
#| label: fig-mean
#| fig-cap: "Percentage agreement on preferences for pension commodification according to mobility trajectory and time (2016, 2018, and 2023)."
#| out-width: '90%'
#| fig-cap-location: bottom
#| echo: false
#| results: asis

g2

@@

```{r}
#| label: fig-reg
#| fig-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification. Coefficient plot of origin-specific ATT estimates comparing mobility versus immobility. Estimates from pooled WLS with doubly robust adjustment, wave fixed effects, and standard errors clustered by individual; bars show 95% confidence intervals."
#| out-width: '90%'
#| fig-cap-location: bottom
#| echo: false
#| results: asis

@@

```{r}
#| label: fig-interact
#| fig-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification, by meritocratic perception. Coefficient plot of origin-specific ATT estimates comparing mobility versus immobility, estimated from interaction models (T × Merit). Points show simple slopes of the mobility effect at low merit and high merit; bars are 95% confidence intervals. Estimates from pooled WLS with doubly robust adjustment, wave fixed effects, and standard errors clustered by individual."
#| out-width: '90%'
#| fig-cap-location: bottom
#| echo: false
#| results: asis

g4
```

>>>>

```{r}
#| label: fig-alluvial
#| fig-cap: "Change in preferences for pension commodification over time (2016, 2018, and 2023)."
#| fig-cap-location: bottom
#| echo: false
#| results: asis
g1 +
  theme(legend.text = element_text(size = 10))
```

@@

```{r}
#| label: fig-mean
#| fig-cap: "Percentage agreement on preferences for pension commodification according to mobility trajectory and time (2016, 2018, and 2023)."
#| out-width: '90%'
#| fig-asp: 0.7
#| fig-cap-location: bottom
#| echo: false
#| results: asis

g2 +
  theme(legend.text = element_text(size = 10))

@@

```{r}
#| label: fig-reg
#| fig-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification. Coefficient plot of origin-specific ATT estimates comparing mobility versus immobility. Estimates from pooled WLS with doubly robust adjustment, wave fixed effects, and standard errors clustered by individual; bars show 95% confidence intervals."
#| out-width: '90%'
#| fig-asp: 0.7
#| fig-cap-location: bottom
#| echo: false
#| results: asis

@@

```{r}
#| label: fig-interact
#| fig-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification, by meritocratic perception. Coefficient plot of origin-specific ATT estimates comparing mobility versus immobility, estimated from interaction models (T × Merit). Points show simple slopes of the mobility effect at low merit and high merit; bars are 95% confidence intervals. Estimates from pooled WLS with doubly robust adjustment, wave fixed effects, and standard errors clustered by individual."
#| out-width: '90%'
#| fig-asp: 0.8
#| fig-cap-location: bottom
#| echo: false
#| results: asis

g4+
  theme(legend.text = element_text(size = 10))
```
